---
title: "Datasets in the BioimageBbs"
author: 
- name: Satoshi Kume
  email: satoshi.kume.1984@gmail.com
date: "`r Sys.Date()`"
graphics: no
package: BioImageDbs, magick
output:
  BiocStyle::html_document:
      toc_float: true
vignette: >
  %\VignetteIndexEntry{Datasets in the BioimageBbs}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{ExperimentHub}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("BioImageDbs_Datasets.Rmd")$mtime`<br />
**Compiled**: `r Sys.time()`

# Fetch Bioimage Datasets from ExperimentHub

The `BioImageDbs` package provides the metadata for all BioImage 
databases in `r Biocpkg("ExperimentHub")`. 

The `BioImageDbs` package provides the metadata for bioimage datasets,
which is preprocessed as array format and saved in
`r Biocpkg("ExperimentHub")`.

# ExperimentHub package

First we load/update the `ExperimentHub` resource.

```{r load-lib, message = FALSE}
library(ExperimentHub)
eh <- ExperimentHub()
```

# Simaple query

We can retrieve only the BioImageDbs tibble files as follows.

```{r echo=TRUE, eval=TRUE}
qr <- query(eh, c("BioImageDbs"))

#Show metadata (e.g. ah_id and title)
qr$ah_id
qr$title
```

# About datasets

## EM_id0001: Mouse brain neurons

```{r echo=TRUE, eval=TRUE}
qr <- query(eh, c("BioImageDbs", "EM_id0001"))

##Show metadata
qr$title

##Import data
#Img_Data <- qr[[1]]
gif_Data <- qr[[2]]
magick::image_read(gif_Data)
```


# Session information {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```


