---
title: "Provide Bio-image Dataset for AnnotationHub"
author: "Satoshi Kume, Kozo Nishida"
date: "`r Sys.Date()`"
graphics: no
package: AHBioImageDbs, knitr
output:
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Provide Bio-image Dataset for AnnotationHub}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
    %\VignetteDepends{AnnotationHub}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Authors**: `r packageDescription("AHPubMedDbs")[["Author"]] `<br />
**Last modified:** `r file.info("pubmed.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Utilization and Prospects for Bioimage Datasets

In recent years, there has been a growing need for data analysis using machine 
learning in the field of biological imaging. 
Machine learning is an inductive approach using data, and the construction of 
models involves the use of image data itself.
Thus, the publication and sharing of bioimage datasets [1], as well as 
knowledge creation by adding metadata to bioimages [2, 3], are important 
issues to be discussed.
Currently, there is still no commonly-used format for publishing bioimage 
datasets. Therefore, different image repositories manage the data in different 
formats (image data itself, and metadata including image format, 
instruments/microscopes, etc.).

In data analysis using those images, it is assumed that several steps of 
image pre-processing will be performed depending on the analysis environment 
used. In fact, the implementation of supervised learning starts with finding 
a repository of bioimage dataset that contains the original images and the 
corresponding supervised labels. Once the repository is found, the image data 
is downloaded from the repository, the data is loaded, and it is prepared in 
a format suitable for the analysis environment. These processes are 
time-consuming before analysis.
Also, in most cases of image repositories, the data is not published in a format 
suitable for reading and processing data in R (.Rdata, csv, etc.). They are 
not easy to use for R users.





# Fetch Bioimage Datasets from `AnnotationHub`

The `AHBioImageDbs` package provides the metadata for all BioImage 
databases in `r Biocpkg("AnnotationHub")`. 

The `AHBioImageDbs` package provides the metadata for bioimage datasets,
which is preprocessed as array format and saved in
`r Biocpkg("AnnotationHub")`.

First we load/update the `AnnotationHub` resource.

```{r load-lib, message = FALSE}
library(AnnotationHub)
ah <- AnnotationHub()
```




Next we list all AHBioImageDbs entries from `AnnotationHub`.



# About the imaging dataset and its metadata

For this dataset in AHBioImageDbs , the published open data on each web-sites 
was used as following; 
1) For the cellular microstructures, the cell tracking, electron microscopy-
based imaging data of mouse brain 
(EM_id0001_Brain_CA1_hippocampus_region_5dTensor.Rda) [4-5], Drosophila brain (EM_id0002_Drosophila_brain_region_5dTensor.Rda) [6-7], mouse B myeloma cell 
line J558L (EM_id0003_J558L_4dTensor.Rda) [8], and The primary human T cell 
isolated from peripheral blood mononuclear cells 
(EM_id0004_PrHudata_4dTensor.Rda) [8]. 
2) For the cell tracking, light microscopy-based imaging data of human HeLa 
cells on a flat glass (ex. LM_id0001_DIC_C2DH_HeLa_4dTensor.Rda) [9], human 
glioblastoma-astrocytoma U373 cells on a polyacrylamide substrate (ex. LM_id0002_PhC_C2DH_U373_4dTensor.Rda) [9], and GFP-GOWT1 mouse stem cells 
(ex. LM_id0003_Fluo_N2DH_GOWT1_4dTensor.Rda) [10]

The detailed information was described in the metadata file of AHBioImageDbs.

# References

1. Williams, E., Moore, J., Li, S.W. et al. Publisher Correction: Image Data Resource: a bioimage data integration and publication platform. Nat Methods 15, 984 (2018). https://doi.org/10.1038/s41592-018-0169-x

2. Kobayashi, N., Kume, S., Lenz, K., & Masuya, H. (2018). RIKEN MetaDatabase: A Database Platform for Health Care and Life Sciences as a Microcosm of Linked Open Data Cloud. International Journal on Semantic Web and Information Systems (IJSWIS), 14(1), 140-164. doi:10.4018/IJSWIS.2018010106

3. Kume S., Masuya H., Maeda M., Suga M., Kataoka Y., Kobayashi N. (2017) Development of Semantic Web-Based Imaging Database for Biological Morphome. In: Wang Z., Turhan AY., Wang K., Zhang X. (eds) Semantic Technology. JIST 2017. Lecture Notes in Computer Science, vol 10675. Springer, Cham. https://doi.org/10.1007/978-3-319-70682-5_19

4. A. Lucchi Y. Li and P. Fua, Learning for Structured Prediction Using Approximate Subgradient Descent with Working Sets, Conference on Computer Vision and Pattern Recognition, 2013.

5. A. Lucchi, K.Smith, R. Achanta, G. Knott, P. Fua, Supervoxel-Based Segmentation of Mitochondria in EM Image Stacks with Learned Shape Features, IEEE Transactions on Medical Imaging, Vol. 30, Nr. 11, October 2011."

6. Cardona A, Saalfeld S, Preibisch S, Schmid B, Cheng A, Pulokas J, Tomancak P, Hartenstein V. 2010. An Integrated Micro- and Macroarchitectural Analysis of the Drosophila Brain by Computer-Assisted Serial Section Electron Microscopy. PLoS Biol 8(10): e1000502. doi:10.1371/journal.pbio.1000502.

7. Ignacio Arganda-Carreras, Srinivas C. Turaga, Daniel R. Berger, Dan Ciresan, Alessandro Giusti, Luca M. Gambardella, Jürgen Schmidhuber, Dmtry Laptev, Sarversh Dwivedi, Joachim M. Buhmann, Ting Liu, Mojtaba Seyedhosseini, Tolga Tasdizen, Lee Kamentsky, Radim Burget, Vaclav Uher, Xiao Tan, Chanming Sun, Tuan D. Pham, Eran Bas, Mustafa G. Uzunbas, Albert Cardona, Johannes Schindelin, and H. Sebastian Seung. Crowdsourcing the creation of image segmentation algorithms for connectomics. Frontiers in Neuroanatomy, vol. 9, no. 142, 2015.

8. Volker Morath, Margret Keuper, Marta Rodriguez-Franco, Sumit Deswal, Gina Fiala, Britta Blumenthal, Daniel Kaschek, Jens Timmer, Gunther Neuhaus, Stephan Ehl, Olaf Ronneberger, Wolfgang Werner A. Schamel: Semi-automatic determination of cell surface areas used in systems biology, Frontiers in Bioscience, Elite, 5, 533-545, January 1, 2013.

9. http://celltrackingchallenge.net/2d-datasets/

10. Bártová E, Šustáčková G, Stixová L, Kozubek S, Legartová S, et al. (2011) 
Recruitment of Oct4 Protein to UV-Damaged Chromatin in Embryonic Stem Cells. 
PLOS ONE 6(12): e27281. https://doi.org/10.1371/journal.pone.0027281

