---
title: "make-data_for_v02"
author: 
- name: Satoshi Kume
  email: satoshi.kume.1984@gmail.com
date: "`r Sys.Date()`"
graphics: no
package: BioImageDbs
output:
  BiocStyle::html_document:
      toc_float: false
vignette: >
  %\VignetteIndexEntry{make-data_for_v02}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{ExperimentHub}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---


```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("make-data_for_v02.Rmd")$mtime`<br />
**Compiled**: `r date()`

**This script for the v02 dataset**

# Load the package

```{r echo=TRUE, eval=FALSE}
#Install
#rm(list=ls())
devtools::install_github( "kumeS/BioImageDbs", force = TRUE )
library(BioImageDbs)

#Source
source(system.file("scripts", "ImgProc_for_v02.R", package="BioImageDbs"))
source(system.file("scripts", "ImageView_for_v02.R", package="BioImageDbs"))
```

# Convert the images to the array data in R

## SampleDataset_cats_segmentation

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataFolder <- "SampleDataset_cats_segmentation"
DataPath <- "./BioImageDbs_02_Dataset_v02"
WIDTH00 <- 128; HEIGHT00 <- 128; CHANNELS01 <- 3; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path="OriginalData",
                  GroundTruth_path="GroundTruth_8b",
                  FileName=paste0(DataFolder, "_4dTensor"),
                  Binary=FALSE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, "_4dTensor.Rds"),
                        destinations=DataPath, overwrite = TRUE)
#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, "_4dTensor.Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, "_4dTensor_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, "_4dTensor_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="SampleDataset_cats_segmentation.rds",
  Description="4D arrays for cat-segmentation dataset provided by @taashi. Training dataset is 60 image pairs and test dataset is 20 image pairs. Image size is 128x128 px. Original images are RGB color.",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="Apr 9 2018",
  Species="Felis catus",
  TaxonomyId="9685",
  Coordinate_1_based="NA",
  DataProvider="https://github.com/taashi-s/UNet_Keras",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/SampleDataset_cats_segmentation.rds",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="SampleDataset_cats_segmentation.gif",
  Description="A animation file (.gif) of the train dataset of SampleDataset_cats_segmentation.rds",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="Apr 9 2018",
  Species="Felis catus",
  TaxonomyId="9685",
  Coordinate_1_based="NA",
  DataProvider="https://github.com/taashi-s/UNet_Keras",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/SampleDataset_cats_segmentation.gif",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

## EM_id0005_Mouse_Kidney_2D

### Mito_OriginalData_512 / Mito_GroundTruth_512

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0005_Mouse_Kidney_2D"
DataFolder_Name <- "_Mito512_4dTensor"
Original_path="Mito_OriginalData_512"
GroundTruth_path="Mito_GroundTruth_512"
WIDTH00 <- 512; HEIGHT00 <- 512; CHANNELS01 <- 1; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=FALSE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)
#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### MitoAll_OriginalData_1024 / MitoAll_GroundTruth_1024

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0005_Mouse_Kidney_2D"
DataFolder_Name <- "_Mito1024_4dTensor"
Original_path="MitoAll_OriginalData_1024"
GroundTruth_path="MitoAll_GroundTruth_1024"
WIDTH00 <- 1024; HEIGHT00 <- 1024; CHANNELS01 <- 1; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)
#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### Nuc_OriginalData_1024 / Nuc_GroundTruth_1024

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0005_Mouse_Kidney_2D"
DataFolder_Name <- "_Nuc1024_4dTensor"
Original_path="Nuc_OriginalData_1024"
GroundTruth_path="Nuc_GroundTruth_1024"
WIDTH00 <- 1024; HEIGHT00 <- 1024; CHANNELS01 <- 1; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)
#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

## EM_id0006_Rat_Liver_2D

### Mito_OriginalData_256 / Mito_GroundTruth_256

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0006_Rat_Liver_2D"
DataFolder_Name <- "_Mito256_4dTensor"
Original_path="Mito_OriginalData_256"
GroundTruth_path="Mito_GroundTruth_256"
WIDTH00 <- 256 ; HEIGHT00 <- 256 ; CHANNELS01 <- 1 ; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)
#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### Mito_OriginalData_512 / Mito_GroundTruth_512

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0006_Rat_Liver_2D"
DataFolder_Name <- "_Mito512_4dTensor"
Original_path="Mito_OriginalData_512"
GroundTruth_path="Mito_GroundTruth_512"
WIDTH00 <- 512 ; HEIGHT00 <- 512 ; CHANNELS01 <- 1 ; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)

#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### Mito_OriginalData_1024 / Mito_GroundTruth_1024

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0006_Rat_Liver_2D"
DataFolder_Name <- "_Mito1024_4dTensor"
Original_path="Mito_OriginalData_1024"
GroundTruth_path="Mito_GroundTruth_1024"
WIDTH00 <- 1024 ; HEIGHT00 <- 1024 ; CHANNELS01 <- 1 ; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)

#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### Mito_OriginalData_1024 / Mito_GroundTruth_1024 (Mito512c_4dTensor)

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0006_Rat_Liver_2D"
DataFolder_Name <- "_Mito512c_4dTensor"
Original_path="Mito_OriginalData_1024"
GroundTruth_path="Mito_GroundTruth_1024"
WIDTH00 <- 512 ; HEIGHT00 <- 512 ; CHANNELS01 <- 1 ; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)

#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```

### Nuc_OriginalData_1024 / Nuc_GroundTruth_1024

```{r echo=TRUE, eval=FALSE}
#Set parameters
DataPath <- "./BioImageDbs_02_Dataset_v02"
DataFolder <- "EM_id0006_Rat_Liver_2D"
DataFolder_Name <- "_Nuc1024_4dTensor"
Original_path="Nuc_OriginalData_1024"
GroundTruth_path="Nuc_GroundTruth_1024"
WIDTH00 <- 1024 ; HEIGHT00 <- 1024 ; CHANNELS01 <- 1 ; CHANNELS02 <- 1

#Run the conversion
DataImport_2d_seg(WIDTH = WIDTH00, HEIGHT = HEIGHT00,
                  CHANNELS01 = CHANNELS01, CHANNELS02 = CHANNELS02,
                  data=DataPath,
                  path01=DataFolder,
                  Original_path=Original_path,
                  GroundTruth_path=GroundTruth_path,
                  FileName=paste0(DataFolder, DataFolder_Name),
                  Binary=TRUE)

#Move data
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, ".Rds"),
                        destinations=DataPath, overwrite = TRUE)

#Read data
Dat <- readRDS( paste0(DataPath, "/", DataFolder, DataFolder_Name, ".Rds") )
str(Dat)
table(Dat$Train$Train_GroundTruth)
table(Dat$Test$Test_GroundTruth)

ImageView2D(Dat$Train, Interval=0.8, Name=paste0(DataFolder, DataFolder_Name, "_train_dataset"))
filesstrings::file.move(files=paste0(DataFolder, DataFolder_Name, "_train_dataset.gif"),
                        destinations=DataPath, overwrite = TRUE)

Meta.Rds <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="List",
  DispatchClass="Rds",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")
Meta.gif <- data.frame(
  Title="",
  Description="",	
  BiocVersion="3.13",
  Genome="NA",
  SourceType="PNG",
  SourceUrl="https://github.com/kumeS/BioImageDbs",
  SourceVersion="",
  Species="",
  TaxonomyId="",
  Coordinate_1_based="NA",
  DataProvider="",
  Maintainer="Satoshi Kume <satoshi.kume.1984@gmail.com>",
  RDataClass="magick-image",
  DispatchClass="FilePath",
  RDataPath="BioImageDbs/v02/",
  Tags="segmentation:2D images:SampleImage")

readr::write_csv(Meta.Rds, file = "Metadata.csv", append = T, col_names = F)
readr::write_csv(Meta.gif, file = "Metadata.csv", append = T, col_names = F)

```



